---
title: "p8105_hw4_p1_ym2649"
author: "Yutian Mu"
date: "10/23/2017"
output: html_document
---

```{r load_libraries}
library(tidyverse)
library(janitor)
```

```{r read_data}
pups_data = read_csv("./FAS_pups.csv", col_types = "ciiiii") %>%
clean_names() %>%
gather(key = development_landmark, value = PD_outcome, pd_ears:pd_walk)
```

```{r plot by Zhuyu Qiu}
ggplot(pups_data, aes(x = development_landmark, y = PD_outcome)) + 
  geom_violin(aes(fill = development_landmark), color = "blue", alpha = .5)+geom_boxplot(width=0.03)+labs(x ="development_landmark", y = "pd_outcome", title = "The relationship between developmental landmark and post-natal days")
```

From this plot, we can see that the distributions of post-natal days for each the developmental landmark have huge difference. pd_ears has the least post-natal days, while pd_eyes has the most. And the pd_pivot has the widest range, while pd_ears has the narrowest. And all the distributions have the obvious waved distribution except the pd_pivot, meaning there are clusters in the distribution for each developmental landmark.